Spoken Corpus of Karel Mako\v{n}

### 2018-04-13 2018-clarin-pisa/makon-data.tex
citations clarin2018

@@

Most of the previous work was focused on acquiring the automatic transcription
and development of a web interface to allow users to access the talks and
provide corrections to the existing transcription, in order to have high-quality
transcription as well as to gather more training data.

@@

The author of the talks, Mr. Karel Mako\v{n} *1912 \textdagger{}1993, was giving
talks in a strife to share his awareness of the proverbial meaning of life and
to give a manual to eternal life after his release from a concentration camp
during the WWII.

@@

We don't have the resources needed to manually annotate the corpus like
e.g.~\ref{japsponta}, but there are lay
volunteers willing to work on the project for the cause of tending Mako\v{n}'s
legacy.

@@

The word error rate on our test set is currently 42\% but it is probably lower
on clean recordings and also most mistakes are in word endings, so the meaning
is comprehensible. I am currently working on a DNN acoustic model, so chances
are the ASR score will soon rise.

@@

A list of recurring topics and their identification in the sound files is a
point of future work.
We can take the current transcription %and the few notes some listeners made
%about topics and their alignment with the audio
as a source for a baseline.
Topic is inherently a vague concept %, which I shall address when I focus on it
but for the baseline evaluation, we can take a look at some easily defined cases
like named entities. The ease about them is that we can look for their specific
word form and if it is not found, then it means the transcription is not
covering it.

@@

\begin{thebibliography}{}

\bibitem[\protect\citename{Aho and Ullman}1972]{Aho:72}
Alfred~V. Aho and Jeffrey~D. Ullman.
\newblock 1972.
\newblock {\em The Theory of Parsing, Translation and Compiling}, volume~1.
\newblock Prentice-{Hall}, Englewood Cliffs, NJ.

\bibitem[\protect\citename{{American Psychological Association}}1983]{APA:83}
{American Psychological Association}.
\newblock 1983.
\newblock {\em Publications Manual}.
\newblock American Psychological Association, Washington, DC.

\bibitem[\protect\citename{{Association for Computing Machinery}}1983]{ACM:83}
{Association for Computing Machinery}.
\newblock 1983.
\newblock {\em Computing Reviews}, 24(11):503--512.

\bibitem[\protect\citename{Chandra \bgroup et al.\egroup }1981]{Chandra:81}
Ashok~K. Chandra, Dexter~C. Kozen, and Larry~J. Stockmeyer.
\newblock 1981.
\newblock Alternation.
\newblock {\em Journal of the Association for Computing Machinery},
  28(1):114--133.

\bibitem[\protect\citename{Gusfield}1997]{Gusfield:97}
Dan Gusfield.
\newblock 1997.
\newblock {\em Algorithms on Strings, Trees and Sequences}.
\newblock Cambridge University Press, Cambridge, UK.

\end{thebibliography}

>>>>

\begin{filecontents}{citace.bib}
@inproceedings{maekawa2000spontaneous,
  title={Spontaneous Speech Corpus of Japanese.},
  author={Maekawa, Kikuo and Koiso, Hanae and Furui, Sadaoki and Isahara, Hitoshi},
  booktitle={LREC},
  year={2000},
  organization={Citeseer}
}
@inproceedings{kruuza2012making,
  title={Making Community and ASR Join Forces in Web Environment},
  author={Kr\r{u}za, Old{\v{r}}ich and Peterek, Nino},
  booktitle={International Conference on Text, Speech and Dialogue},
  pages={415--421},
  year={2012},
  organization={Springer}
}
@article{hajek2007cesky,
  title={\v{C}esk\'{y} mystik Karel Mako\v{n}},
  author={Jurik H\'{a}jek},
  journal={Dingir},
  year={2007},
  volume={2007/4},
  pages={142--143},
  publisher={Dingir, s.r.o.},
  ISSN={1212-1371},
  editor={Zden\v{e}k Vojt\'{i}\v{s}ek}
}
\end{filecontents}

@@

Most of the previous work was focused on acquiring the automatic transcription
and development of a web interface~\cite{kruuza2012making} to allow users to
access the talks and provide corrections to the existing transcription, in order
to have high-quality transcription as well as to gather more training data.

@@

The author of the talks, Mr. Karel Mako\v{n}~\cite{hajek2007cesky} *1912
\textdagger{}1993, was giving talks in a strife to share his awareness of the
proverbial meaning of life and to give a manual to eternal life after his
release from a concentration camp during the WWII.

@@

We don't have the resources needed to manually annotate the corpus like
e.g.~\cite{maekawa2000spontaneous}, but there are lay
volunteers willing to work on the project for the cause of tending Mako\v{n}'s
legacy.

@@

The word error rate on our test set is currently 42\% but it is probably lower
on clean recordings and also most mistakes are in word endings, so the meaning
is comprehensible. I am currently working on a DNN acoustic
model~\cite{hannun2014deep}, so chances are the ASR score will soon rise.

@@

A list of recurring topics and their identification in the sound files is a
point of future work with similarities to~\cite{skorkovska2011automatic}.
We can take the current transcription %and the few notes some listeners made
%about topics and their alignment with the audio
as a source for a baseline.
Topic is inherently a vague concept %, which I shall address when I focus on it
but for the baseline evaluation, we can take a look at some easily defined cases
like named entities. The ease about them is that we can look for their specific
word form and if it is not found, then it means the transcription is not
covering it.

@@

\bibliography{citace}
